Response to the defense feedback

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

If the input-sensitive data can affect the victim program's control flow, then an attacker can infer the sensitive data by observing the control flow during the execution. Figure~\ref{fig:chapter3:cf}(a) shows such an example. The function takes a public value \textsf{m} and a secret \textsf{k} as the inputs. The code at line 2 ensures that the lower 7 bits of the value \textsf{k} do not affect the value \textsf{b}. However, depending on the value of \text{m}, the code snippet in Figure~\ref{fig:chapter3:cf}(a) may have a leakage site. If the eighth bit of \textsf{m} is 1, then an attacker can infer the eighth bit of \textsf{k} by observing the branch at line 4 or line 6. The right figure shows the corresponding machine code. It has a conditional jump instruction \textsf{jne}. The sensitive input \textsf{k} can affect the program counter (the \textsf{rip} register), which is the root cause of the side-channel leakages.

However, the if-else branch does not always indicate there is a potential leakage site. Figure~\ref{fig:chapter3:cf}(b) shows a different situation. While the sensitive input \textsf{k} can affect the if-else branch, the compiler removes the branch with a conditional set instruction.  The opposite situation is the same. For example, recent work tries to use bit masking to rewrite the program with control flows. However, for some situations~\cite{Coppens:2009:PMT:1607723.1608124}, compilers (e.g., GCC) optimize the code too much (from a security view) and remove the unnecessary copy by reintroducing conditional moves.
\subsubsection{Data Flow}
\begin{figure}[ht]
  \begin{minipage}{0.4\linewidth}
    \begin{lstlisting}[xleftmargin=.15\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t T[128];
...
int example3(uint8_t k, uint32_t m){
  uint32_t index = m;
  index = index + k % 128;
  uint8_t t = T[index];
  ...
}
\end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{0.4\linewidth}
    \begin{lstlisting}[xleftmargin=.15\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
...
lea    edx, [addr_T]
mov    eax, [addr_k]
and    eax, 0x7f
add    eax, [addr_m]
movzx  eax, [addr_T + eax*1]
...
\end{lstlisting}
  \end{minipage}\caption*{(a) A True Leakage}

>>>>

If the input-sensitive data can affect the victim program's control flow, then an attacker can infer the sensitive data by observing the control flow during the execution. Figure~\ref{fig:chapter3:cf}(a) shows such an example. The function takes a public value \textsf{m} and a secret \textsf{k} as the inputs. The code at line 2 ensures that the lower 7 bits of the value \textsf{k} do not affect the value \textsf{b}. However, depending on the value of \text{m}, the code snippet in Figure~\ref{fig:chapter3:cf}(a) may have a leakage site. If the eighth bit of \textsf{m} is 1, then an attacker can infer the eighth bit of \textsf{k} by observing the branch at line 4 or line 6. The right figure shows the corresponding machine code. It has a conditional jump instruction \textsf{jne}. The sensitive input \textsf{k} can affect the program counter (the \textsf{rip} register), which is the root cause of the side-channel leakage here.

However, a if-else branch does not always indicate there is a potential leakage site. Figure~\ref{fig:chapter3:cf}(b) shows a different situation. While the sensitive input \textsf{k} can affect the if-else branch, the compiler removes the branch with a conditional set instruction.  The opposite situation is the same. For example, recent work tries to use bit masking to rewrite the program with control flows. However, for some situations~\cite{Coppens:2009:PMT:1607723.1608124}, compilers (e.g., GCC) optimize the code too much (from a security view) and remove the unnecessary copy by reintroducing conditional jump instructions.
\subsubsection{Data Flow}
\begin{figure}[ht]
  \begin{minipage}{0.4\linewidth}
    \begin{lstlisting}[xleftmargin=.15\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t T[128];
...
int example3(uint8_t k, uint32_t m){
  uint32_t index = m;
  index = index + k % 128;
  uint8_t t = T[index];
  ...
}
\end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{0.4\linewidth}
    \begin{lstlisting}[xleftmargin=.15\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
...
lea    edx, [addr_T]
mov    eax, [addr_k]
and    eax, 0x7f
add    eax, [addr_m]
movzx  eax, [addr_T + eax*1]
...
\end{lstlisting}
  \end{minipage}\caption*{(a) A True Leakage}
